Finch: Sparse and Structured Array Programming with Control Flow

### 2024-04-01 sections/related.tex
Update on Overleaf.

\paragraph{Dense Libraries:}

@@

%% Libraries: Numpy, LAPACK, blas, graphblas, SplAtt, Scipy, Petsc, 
%% Languages: Halide, Lift, TVM, OptiML
%% Languages: Lgen/Spiral, LAMapping system,
%% languages sparse: TVM Sparse, Tiachi, SPF, TACO, Stut, various extensiosn to TACO,
%% SQL: HyPer, SDQL + Formats, Vectorwise, Morphesu,

>>>>

\paragraph{Dense Libraries:} There are many well known libraries that specialize in dense computations, exemplified by BLAS, though several BLAS routines are specialized to symmetric, hermitian, and triangular matrices~\cite{Anderson1999}.
%
This pattern is carried over into well known dense array libraries that use BLAS, exemplified by Numpy

%

@@

%% Libraries: Numpy, LAPACK, blas, graphblas, SplAtt, Scipy, Petsc, Graph libraries (ligraph, lagraph,...)
%% Languages: Halide, Lift, TVM, OptiML
%% Languages: Lgen/Spiral, LAMapping system,
%% languages sparse: TVM Sparse, Tiachi, SPF, TACO, Stut, various extensiosn to TACO, Graphit
%% SQL: HyPer, SDQL + Formats, Vectorwise, Morphesu,
